Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
Took out rounding the market values

################### Org Reactive Element####################################

@@

################### Persona Reactive Element####################################

@@

@@

<!-- Persona Inputs  -->
<!-- ================================================= -->

<!-- ## Persona Inputs -->

```{r persona betas}

@@

  # Expected Utility
  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)

  # Market Share
  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

@@

  # Expected Utility
  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)

  # Market Share
  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))

@@

  # Expected Utility
  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)

  # Market Share
  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))

@@

<!-- Organizational Tabs -->

>>>>

################### Org Reactive Element ####################################

@@

################### Persona Reactive Element ####################################

@@

<!-- Practice Code -->

@@

<!-- Persona Inputs -->
```{r persona betas}

@@

  # Expected Utility
  ai_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta1))
  gp_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta1))
  ox_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta1))
  rc_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta1))

  # Market Share
  ai_rate1 <- 100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
  gp_rate1 <- 100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
  ox_rate1 <- 100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)
  rc_rate1 <- 100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1)

@@

  # Expected Utility
  ai_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta2))
  gp_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta2))
  ox_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta2))
  rc_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta2))

  # Market Share
  ai_rate2 <- 100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
  gp_rate2 <- 100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
  ox_rate2 <- 100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)
  rc_rate2 <- 100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2)

@@

  # Expected Utility
  ai_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_beta3))
  gp_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_beta3))
  ox_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_beta3))
  rc_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_beta3))

  # Market Share
  ai_rate3 <- 100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
  gp_rate3 <- 100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
  ox_rate3 <- 100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)
  rc_rate3 <- 100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3)

@@

<!-- Persona and Organizational Tabs -->
